---
title: "MakeCodeBook"
output: html_document
---

## CodeBook

For the peer evaluted assignment of the "Getting and Cleaning Data" (week 4) course on Coursera, we are asked to produce a CodeBook, that "*describes the variables, the data, and any transformations or work that you performed to clean up the data called CodeBook.md*".

### Variables (list and description)





| Variable name | Description |
| :--------- | :------------------------------------------------- |
| subject | The ID number for the subject who performed the activity. the range is 1 to 30. |
| activity | Name of the activity |
| domain | The domain can be either time or frequency (Time or Freq) |
| instrument | Measuring instrument (Accelerometer or Gyroscope) |
| acceleration | Acceleration signal (Body or Gravity) |
| variable | Either the mean or the standard deviation (mean or SD) |
| jerk | Jerk signal |
| magnitude | Magnitude of the signals calculated using the Euclidean norm. |
| axis | axial signal in the X, Y and Z directions (X, Y, or Z). |
| count | Count of data points used to compute the average. |
| average | Average of each variable for each activity and each subject. |

### Structure of the data
```{r}
str(tidyData)
```

### List of variables
```{r}
names(tidyData)
```

### Show a few rows of the data set
```{r}
head(tidyData)
```

### Summary of variables
```{r}
summary(tidyData)
```

### Save to file
Finally we dave the data to a tab-delimetered file, that we shall call HumanActivityRecognitionUsingSmartphonesDataSet.txt.

```{r}
f <- file.path(path, "HumanActivityRecognitionUsingSmartphonesDataSet.txt")
write.table(tidyData, f, quote = FALSE, sep = "\t", row.names = FALSE)
```